Figures

### 2019-07-12 figures/08_exploratory_dotplot.Rmd
make dotplot legend vertical

plot_opts <- theme_cowplot() +
  theme(axis.title.y = element_blank(), 
                   axis.text = element_text(size = 8), 
                   legend.position = 0)

@@

# head(prep_dotplot(dt_tp, "tp"))
# show_col(brewer_pal("div", "Set1")(4))                   
gg_tp <-  ggplot(data = dt_tp) + 
    geom_point(aes(x = tp, y = pretty, color = category)) + 
    scale_color_brewer(palette = "Set1") +
    xlim(0, 0.6) +
    plot_opts
gg_tn <- ggplot(data = dt_tn) + 
    geom_point(aes(x = tn, y = pretty, color = category)) +
    scale_color_brewer(palette = "Set1") +
    xlim(0, 0.6) +
    plot_opts
legend_b <- get_legend(gg_tp + 
                         theme(legend.position="bottom", 
                               legend.justification = "center", 
                               legend.text = element_text(size = 10), 
                               legend.title = element_blank()))
plot_grid(
  plot_grid(gg_tp, gg_tn), 
  legend_b, ncol = 1, rel_heights = c(1, 0.1))

>>>>

@@

# head(prep_dotplot(dt_tp, "tp"))
# show_col(brewer_pal("div", "Set1")(4))                   
plot_opts <- theme_cowplot() +
  theme(axis.title.y = element_blank(), 
        axis.text = element_text(size = 8), 
        axis.title.x = element_blank())

gg_tp <-  ggplot(data = dt_tp) + 
    geom_point(aes(x = tp, y = pretty, color = category)) + 
    scale_color_brewer(palette = "Set1") +
    xlim(0, 0.6) +
    plot_opts +
  theme(legend.text = element_text(size = 8), 
        legend.position = c(0.53, 0.23), 
        legend.box.background = element_rect(color = "black"), 
        legend.title = element_blank())
gg_tn <- ggplot(data = dt_tn) + 
    geom_point(aes(x = tn, y = pretty, color = category)) +
    scale_color_brewer(palette = "Set1") +
    xlim(0, 0.6) +
    plot_opts +
  theme(legend.position = 0)

plot_grid(NULL, 
plot_grid(gg_tp, NULL,
          gg_tn, rel_widths = c(1, 0.2, 1), nrow = 1, 
          labels = c("TP", "", "TN"), 
          label_x = c(0.6, 0.5, 0.6), 
          label_y = c(1.05, 1.1, 1.05)), 
ncol = 1, rel_heights = c(0.07, 1))
